Expand Big, Then Shrink: An Automatic Way to Generating Efficient Super Resolution Model

### 2023-04-06 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
update
Add refs into esrx4paper

Designing an efficient model is non-trivial and always tedious. On one hand, lots of existing work look for insights for reducing FLOPs on operations but which always ignores realistic execution on chip. On the other hand, the macro architecture design of model is also important such as using multiple connections, multiple resolutions, and local sharing. The space to design a SOTA model is too large and it's always fatiguing to update model with complex design over and over.

@@

\begin{itemize}
    \item Discussing on how to design an efficient model in an automatic way.
    \item Proposing \"Expand Big, Then Shrink\" method to automatic adapting an old SOTA model to a new bigger dataset which is an efficient way to design new model.
    \item Evaluating our method on main stream datasets and compared our results with other peers in NTIRE-ESRX4 challenge.
\end{itemize}

@@

Efficient insights are not easy to find and always ignored some important factors in the advanced computing platforms and due to good performance in theory but bad performance in reality which can happen on running MobileNet on different platforms.

@@

We used simple universal scaling methods to expand and shrink model structure but still achieving better accuracy-speed trade-off rather than the original model and the most of peers. On one hand, the way we used to expand model is based on width-multiplier which changed the width of all layers with a same scale. On the other hand, the way we used to shrink is a simple $\mathcal{L}1$ norm based pruner and also shrink all layers with a same scale. This result has proven the effectiveness and potency of the idea of "Expand and Shrink" scaling method.

>>>>

Designing an efficient model is non-trivial and always tedious. On one hand, lots of existing work look for insights for reducing FLOPs on operations but which always ignores realistic execution on chip\cite{sandler2018mobilenetv2}\cite{chen2023run}. On the other hand, the macro architecture design of model is also important such as using multiple connections\cite{chollet2017xception}, multiple resolutions\cite{girshick2015fast}, and local sharing\cite{liu2021swin}. The space to design a SOTA model is too large and it's always fatiguing to update model with complex design over and over.

@@

\begin{itemize}
    \item Discussing on how to design an efficient model in an automatic way.
    \item Proposing "Expand Big, Then Shrink" method to automatic adapting an old SOTA model to a new bigger dataset which is an efficient way to design new model.
    \item Evaluating our method on main stream datasets.
\end{itemize}

@@

Efficient insights are not easy to find and always ignored some important factors in the advanced computing platforms and due to good performance in theory but bad performance in reality which can happen on running MobileNet\cite{sandler2018mobilenetv2} on different platforms.

@@

We used simple universal scaling methods\cite{tan2019efficientnet} to expand and shrink model structure but still achieving better accuracy-speed trade-off rather than the original model and the most of peers. On one hand, the way we used to expand model is based on width-multiplier which changed the width of all layers with a same scale. On the other hand, the way we used to shrink is a simple $\mathcal{L}1$ norm based pruner and also shrink all layers with a same scale. This result has proven the effectiveness and potency of the idea of "Expand and Shrink" scaling method.
